---
output: github_document
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fatRats


The goal of fatRats is to help data scientists and statisticians handling raw data and primarily handling lab data. We have created functions to help in the data cleaning process by higlighting errors in data cleaning and identify what changes may need to be made. All that the package requires for useage is a dataframe. The rest of the package is designed to be very easy to use. We recommend either reading in your files as a CSV or if you have an excel spreadsheet, be sure to read in the correct sheet before you get started.

## Installation

You can install the development version of fatRats from [GitHub](https://github.com/) with:

```{r,warning=FALSE}
install.packages("devtools")
devtools::install_github("nkchebat/stat108project2")
```


## Example 1

This is a basic example which shows you how to use the plot_outliers function. This function is very useful if you are trying to check if your data seems reasonable. If you have any datapoints show up in red on the plot, you may want to go back to your data and ensure that there were no typos. 

```{r example 1, warning=FALSE}
library(fatRats)
plot_outliers(data_weight,"Body.Weight.1")
```

## Example 2

This is a basic example which shows you how to use the check_trend function. This function is useful for checking if there are major errors in your data. If you are observing an experiment with trends over time, this will allow you to check whether or not the data follows the trend you expect. You can then check which data points go against the trend in the table below.

```{r example 2,warning=FALSE}
library(fatRats)
increase_decrease(data_weight, "Body.Weight.1", "Body.Weight.2", "increase")
```





